---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vcovSUR

<!-- badges: start -->
<!-- badges: end -->

The goal of vcovSUR is to allow estimation of the variance-covariance matrix and perform hypotheses tests of [multiple regression equations](https://en.wikipedia.org/wiki/Seemingly_unrelated_regressions). 

This package was inspired by Peter Hull's tweet on 'stacking' regressions to compare coefficients across estimates: https://twitter.com/instrumenthull/status/1492915860763250691. Instead of needing to stack the regressions (which is tedious and easy to mess-up), you can use estimate each regression separately and then use `vcovSUR` to estimate the variance-covariance matrix of the coefficients or `sur_hypotheses` to conduct hypothesis tests *across regression specifications*.


## Installation

You can install the development version of vcovSUR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kylebutts/vcovSUR")
```

## Example

Consider running two regressions with different outcome variables. For our example, we will use the `CASchools` dataset from the `{AER}` package. The dataset contains data on test performance, school characteristics and student demographic backgrounds for school districts in California. Each row is a school.

We want to see if the correlation between percent of students qualifying for reduced-price lunch (`lunch`) and test scores differ between the reading score (`read`) and the math score (`math`).

```{r initial-regressions}
library(vcovSUR)
library(fixest)
data("CASchools", package = "AER")
CASchools$obs_id <- 1:nrow(CASchools)

(est_read <- feols(read ~ lunch, data = CASchools))
(est_math <- feols(math ~ lunch, data = CASchools))
```

Since we are using the same sample for both equations, there is likely a correlation between the error terms in each equation (shocks that impact reading scores for a school also are likely impacting math scores). We can estimate the variance-covariance matrix of estimates *across regression equations* using `vcovSUR`. Note that we need to specify the `cluster` argument to indicate which observations we think could have correlated error terms across regressions. This could be a variable for each observation or some higher level grouping variable (e.g. state, county, etc.). 

Note that this works even if the dataset used in each regression differs. For example, you might have two subsamples (e.g. male and females) but you cluster at the county level to allow county-level shocks to be common across the subsamples. 

```{r vcovSUR-example}
# No correlation between the coefficients since we are not clustering
vcovSUR(list(est_read, est_math))

# Correlation between the coefficients since we are clustering by `obs_id`
vcovSUR(list(est_read, est_math), cluster = "obs_id")
```

With the joint variance-covariance matrix, we can perform tests across regression specifications. However, this is a bit of a pain to do manually, so I have included the `sur_hypotheses` function which is a light wrapper around `hypotheses` from the [`marginaleffects` package](https://vincentarelbundock.github.io/marginaleffects/articles/hypothesis.html). The first two arguments are the same as `vcovSUR`, namely the list of estimates and the cluster variable name. 

The third argument is a string of the hypothesis to test. Since there are multiple regressions and you need to be able specify which regression you want a coefficient from (is it test from read or math?), I suffix each coefficient name with `_#` where the `#` corresponds to the position of the estimate in the `ests` list. Here's an example testing if the coefficient on `lunch` is the same across specifications:

```{r sur_hypotheses-example}
sur_hypotheses(
  list(est_read, est_math), cluster = "obs_id",
  hypothesis = "lunch_1 = lunch_2"
)
```


### `fixest_multi`

You can also include `fixest_multi` objects in the `ests` parameter, and they will be numbered based on the order in `c()`. 

```{r fixest_multi-example}
est_multi <- feols(c(read, math) ~ lunch, CASchools)

sur_hypotheses(
  est_multi, cluster = "obs_id",
  hypothesis = "lunch_1 = lunch_2"
)
```
